Randomization Examples using `okcupiddata` `profiles` data

### 2018-03-30 inst/doc/profiles_examples.Rmd
Tweak pkgdown

The `okcupiddata` is thought by some to be controversial. Its use here is only
to check for a variety of different variable types and levels. It will remain only in this
"cutting edge" version of the package as we continue to add and test examples.

@@

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  # Only "right" or "greater" as options here
  visualize(obs_stat = obs_diff, direction = "greater")
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize(obs_stat = obs_diff, direction = "right")
```

>>>>

There has been some recent [controversy](https://www.wired.com/2016/05/okcupid-study-reveals-perils-big-data-science/) 
surrounding data of this sort similar to what is given in the {okcupiddata}
package. Explicit permission was obtained from OkCupid and usernames were not
included in the data set for that package. Its use here is only
to check for a variety of different variable types and levels. It will remain 
only in this "cutting edge" version of the package as we continue to add 
and test examples.

@@

```{r}
F_hat <- anova(
               aov(formula = age ~ status, data = prof_small)
               )$`F value`[1]
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  # Only "right" or "greater" as options here
  visualize(obs_stat = F_hat, direction = "greater")
```

@@

```{r}
slope_hat <- lm(age ~ height, data = prof_small) %>% 
  broom::tidy() %>% 
  filter(term == "height") %>% 
  select(estimate) %>% 
  pull()
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize(obs_stat = slope_hat, direction = "both")
```
